---
title: "Week 11: Lab - Build Your Own Shiny App"
author: 'Jonathan Forte'
date: '3/30/23'
output: html_document
---

---

# Instructions
Create a scatter plot interactive application. In this application, use the 
census data from earlier in the book, and let the user determine the X-axis, 
the Y-axis, the color (optional), and the size based on what the user would 
like to see. To do this, you will need multiple-choice menus, one for each 
selection the user needs to make. You can do this by following the direction 
written in the text book. Enjoy. 

**For your information:**   
The data is available through this link: 

* http://www2.census.gov/programs-surveys/popest/tables/2010-2011/state/totals/nst-est2011-01.csv


Add all of your libraries that you use for this assignment here.
```{r setup}
# Add your library below.
library(shiny)
library(ggplot2)
library(rsconnect)
```

---

# Step 1 - Build the UI
Build the UI below.

```{r, "Step 1"}
census <- read.csv("data/cleanedCensus.csv")

ui <- fluidPage(
  # Write your code here.
  sidebarLayout(
    sidebarPanel(
      selectInput(
        inputId = "y", label = "Y-axis:", 
        choices = c("april10census", "april10base", "july10pop", "july11pop"),
        selected = "april10census"
      ),
      selectInput(
        inputId = "x", label = "X-axis:",
        choices = c("april10census", "april10base", "july10pop", "july11pop"),
        selected = "april10base"
      ),
      selectInput(
        inputId = "z", label = "Color and Size by:",
        choices = c("april10census", "april10base", "july10pop", "july11pop"),
        selected = "july10pop"
      )
      ),
   mainPanel(
        plotOutput(outputId = "scatterplot")
  )
)
)
```

---

# Step 2 - Build the Server
Build the Server below.
```{r, "Step 2"}
server <- function(input, output) {
 # Write your code here.
  output$scatterplot <- renderPlot({
    ggplot(data = census, aes_string(x = input$x, y = input$y, color = input$z, size = input$z)) + geom_point()
  })
}
```

---

# Step 3 - Create the Shiny App
Deploy the shiny app.
```{r, "Step 3"}
# Write your code here.
shinyApp(ui = ui, server = server)
```
